### 2018-06-12 express2018/conclusions.tex
text

\section{Conclusions}

>>>>

\section{To do}

\finish{explain that also up-to techniques for bisimilarity have been
  formalised, including those making use of expansion. 
Point out that an advantage of the formalisation is 
that we can take advantage of results about different 
equivalences/preorders that have similar proofs, even if the proofs
themselves can be tedious and long. Examples are: ....
There are only a few points in which the scripts have to be modified,
and when the execution of the scripts succesfully terminate we have
the guarantee that the proof is completed. Without theorem provers,
the risk of overlooking or missing  small but important details is
high. 
} 
\section{Conclusions}
